FraCaS: Temporal Analysis

### 2020-06-23 paper2020/paper.tex
revise conclusion

\providecommand\ncases[1]{{\ensuremath{^{#1}}}}
\begin{table}[hbt]
  \centering
  \small
\begin{tabularx}{\columnwidth}{Xr@{\,\,}r@{\,\,}r@{\,\,}r@{\,\,}r@{\,\,}r@{\,\,}r}
Section      & {\kern -2em} \#FraCaS
                          & This        & FC2         & FC & MINE & Nut  & LP  \\ \hline
Quantifiers  & 75         & .91        & .96         & .96    & .77  & .53  & .93  \\
             &            & \ncases{74}& \ncases{74} &        &      &      &     \ncases{44} \\
Plurals      & 33         & .64        & .82         & .76    & .67  & .52  & .73 \\
             &            &            &             &     &   &   & \ncases{24} \\
Anaphora     & 28         & .79        & .86         &   -    & -    & -    &  -       \\
Ellipsis     & 52         & .81        & .87         &   -    & -    & -    &  -       \\
Adjectives   & 22         & .95        & .95         & .95    & .68  & .32  & .73 \\
             &            & \ncases{20}&  \ncases{20}&     &   &   &  \ncases{12} \\
Comparatives & 31         & .64        & .87         & .56    & .48  & .45  &  -       \\
Temporal     & 75         & .71        &  -          &   -    &   -  &  -   &  -       \\
Verbs        & 8          & .75        & .75         &   -    & -    & -    &  -       \\
Attitudes    & 13         & .85        & .92         & .85    & .77  & .46  & .92  \\ 
             &            &            &             &        &      &      & \ncases {9}  \\ \hline
Total        & 337        & .78        & .89         & .83    & .69  & .50  & .85  \\
             &            & \ncases{329}& \ncases{259}& \ncases{174}  & \ncases{174}& \ncases{174}& \ncases{89}
  \end{tabularx}
  \caption{Accuracy of our system compared to others.
    ``Ours" refers to the approach presented in this paper. When a
    system does not handle the nominal number of test cases (shown in
    the second column), the actual number of test cases attempted is
    shown below the accuracy figure, in smaller font.  ``FraCoq''
    refers to the work of \citet{bernardy_type-theoretical_2017}. ``MINE" refers
    to the approach of \citet{Mineshima:2015}, ``NUT" to the CCG
    system that utilizes the first-order automated theorem prover
    \textit{nutcracker} \cite{bos:2008}, and ``Langpro"
    to the system presented by \citet{abzianidze_tableau_2015}. A dash
    indicates that no attempt was made for the section. }
  \label{tab:results}
\end{table}
\paragraph{interaction with negation and group readings}
One reason explaining the lower performance of our systems on some
sections of the testsuite is that our interpretation of time interacts
imperfectly with negation and group readings.

The issue is that the quantification introduced by the temporal marker
is outside the negation. For example, the premiss of (038) is
interpreted as ``there exists a time in the past when every delegate
did not finish the report'' --- which is incorrect in this context.
\fracasex{038}{
\item	No delegate finished the report.
\hyp 	Some delegate finished the report on time.
}
%
We stress that such interaction between quantifiers and negation
already occurs without any temporal analysis: one must make a difference
between narrow  and wide scope.\footnote{The literature on wide and narrow scope readings of quantifiers and quantifiers and negation is vast. We direct the reader to \cite{steedman:2012} for a comprehensive and thorough discussion of the relevant issues.} Unfortunately,
the Montagovian system over which we base our implementation does not
support these phenomena. (In fact the FraCaS test suite does not appear to
test if the difference between narrow and wide scoping is handled properly.)
We propose that the situation becomes
quantitatively more difficult to handle with the added complication of
time-quantification, but not fundamentally different.
%
A similar issue occurs with group readings, which are interpreted as
conjunctions. Here, the problem is to solve the order of scoping
between this conjunction and time-interval quantifiers.

\section{Conclusions and Future Work}
\label{sec:conclusion}
\todo{summary of advances}

We have presented a first attempt for a computational approach dealing
with the temporal section of the FraCaS test suite. This is the first
time a system is ran against this section, at the same time, this
concludes our work in handling the whole of the FraCaS test suite
using a combination of a number of well-studied tools: type theory,
parsing using the Grammatical Framework (GF), Monadic Dynamic
Semantics and proof assistant technology (Coq). It achieves an
accuracy of 0.71 on the Temporal Section and 0.78 overall. One of the
things to be looked at is fixing the issues associated with parts of
the test suite that ``broke'' so to say when the temporal analysis was
introduced. Some of these have been already mentioned: interaction of
the temporal variables with group readings and negation.

Another thing we would be willing to try is an extension of the FraCaS test suite that will include more fine-grained examples of lexical and grammatical aspect and  the interaction between those two, for example cases where one needs to actually distinguish between achievements and accomplishments on the basis of their inferential properties:

>>>>

\providecommand\ncases[1]{{\ensuremath{^{#1}}}}
\begin{table}[hbt]
  \centering
  \small
\begin{tabularx}{\columnwidth}{Xr@{\,\,}r@{\,\,}r@{\,\,}r@{\,\,}r@{\,\,}r@{\,\,}r}
Section      & {\kern -2em} \#FraCaS
                          & This        & FC2         & FC & MINE & Nut  & LP  \\ \hline
Quantifiers  & 75         & .91        & .96         & .96    & .77  & .53  & .93  \\
             &            & \ncases{74}& \ncases{74} &        &      &      &     \ncases{44} \\
Plurals      & 33         & .64        & .82         & .76    & .67  & .52  & .73 \\
             &            &            &             &     &   &   & \ncases{24} \\
Anaphora     & 28         & .79        & .86         &   -    & -    & -    &  -       \\
Ellipsis     & 52         & .81        & .87         &   -    & -    & -    &  -       \\
Adjectives   & 22         & .95        & .95         & .95    & .68  & .32  & .73 \\
             &            & \ncases{20}&  \ncases{20}&     &   &   &  \ncases{12} \\
Comparatives & 31         & .64        & .87         & .56    & .48  & .45  &  -       \\
Temporal     & 75         & .71        &  -          &   -    &   -  &  -   &  -       \\
Verbs        & 8          & .75        & .75         &   -    & -    & -    &  -       \\
Attitudes    & 13         & .85        & .92         & .85    & .77  & .46  & .92  \\ 
             &            &            &             &        &      &      & \ncases {9}  \\ \hline
Total        & 337        & .78        & .89         & .83    & .69  & .50  & .85  \\
             &            & \ncases{329}& \ncases{259}& \ncases{174}  & \ncases{174}& \ncases{174}& \ncases{89}
  \end{tabularx}
  \caption{Accuracy of our system compared to others.
    ``Ours" refers to the approach presented in this paper. When a
    system does not handle the nominal number of test cases (shown in
    the second column), the actual number of test cases attempted is
    shown below the accuracy figure, in smaller font.  ``FraCoq''
    refers to the work of \citet{bernardy_type-theoretical_2017}. ``MINE" refers
    to the approach of \citet{Mineshima:2015}, ``NUT" to the CCG
    system that utilizes the first-order automated theorem prover
    \textit{nutcracker} \cite{bos:2008}, and ``Langpro"
    to the system presented by \citet{abzianidze_tableau_2015}. A dash
    indicates that no attempt was made for the section. }
  \label{tab:results}
\end{table}
\paragraph{interaction with negation and group readings}
One reason explaining the lower performance of our system on some
sections of the testsuite is that our interpretation of time interacts
imperfectly with negation and group readings.

The issue is that the quantification introduced by the temporal marker
is outside the negation. For example, the premiss of (038) is
interpreted as ``there exists a time in the past when every delegate
did not finish the report'' --- which is incorrect in this context.
\fracasex{038}{
\item	No delegate finished the report.
\hyp 	Some delegate finished the report on time.
}
%
We stress that such interaction between quantifiers and negation
already occurs without any temporal analysis: one must make a difference
between narrow  and wide scope.\footnote{The literature on wide and narrow scope readings of quantifiers and quantifiers and negation is vast. We direct the reader to \cite{steedman:2012} for a comprehensive and thorough discussion of the relevant issues.} Unfortunately,
the Montagovian system over which we base our implementation does not
support these phenomena. (In fact the FraCaS test suite does not appear to
test if the difference between narrow and wide scoping is handled properly.)
We propose that the situation becomes
quantitatively more difficult to handle with the added complication of
time-quantification, but not fundamentally different.
%
A similar issue occurs with group readings, which are interpreted as
conjunctions. Here, the problem is an improper resolution of scoping
order, between this conjunction and time-interval quantifiers.

\section{Conclusions and Future Work}
\label{sec:conclusion}

We have presented a first attempt for a computational approach dealing
with the temporal section of the FraCaS test suite. To do this, we
have provided a new, simplified taxonomy of aspectual classes for verb
phrases, guided by the applicability of the unicity of action and
temporal subsumption properties.

This paper concludes our work in handling the whole of the FraCaS test
suite using a combination of a number of well-studied tools: type
theory, parsing using the Grammatical Framework (GF), Monadic Dynamic
Semantics and proof assistant technology (Coq). It achieves an
accuracy of 0.71 on the Temporal Section and 0.78 overall.  One of the
things to be looked at is fixing the issues associated with parts of
the test suite that ``broke'' when the temporal analysis was
introduced. Some of these have been already mentioned: interaction of
the temporal variables with group readings and negation.

Another thing we are willing to try is an extension of the FraCaS
test suite that will include more fine-grained examples of lexical and
grammatical aspect and the interaction between those two, for example
cases where one needs to actually distinguish between achievements and
accomplishments on the basis of their inferential properties:
